\documentclass{beamer}

% for themes, etc.
\mode<presentation>
{ \usetheme{Torino} }
%{ \usetheme{boxes} }

\usepackage{times}  % fonts are up to you
\usepackage{graphicx}

% these will be used later in the title page
\title{CHPC WLCG Tier2 Facility}
\author{Sean Murray \\
    CHPC \\
    CSIR 
}
\date{July 7, 2016}

% note: do NOT include a \maketitle line; also note that this title
% material goes BEFORE the \begin{document}

% have this if you'd like a recurring outline
\AtBeginSection[]  % "Beamer, do the following at the start of every section"
{
\begin{frame}<beamer> 
\frametitle{Outline} % make a frame titled "Outline"
\tableofcontents[currentsection]  % show TOC and highlight current section
\end{frame}
}

\begin{document}

% this prints title, author etc. info from above
\begin{frame}
\titlepage
\end{frame}

\section{WLCG}

\begin{frame}
\frametitle{What is the WLCG}

\ldots\ldots\ldots

\end{frame}

\begin{frame}
\frametitle{July 2015}

\end{frame}

\begin{frame}
\frametitle{Commitments}

\end{frame}

\begin{frame}
\frametitle{What is currently delivered}

cpu
storage
network
\end{frame}

\section{Three pillars}

\begin{frame}
\frametitle{Weird Problems}

pic of network from 27 june where the jobs reduce and network cleans up, additionally the over consumption of the network and the associated job errors.

\end{frame}

\begin{frame}
  \frametitle{Current hardware}
  50 nodes of 48 cores 192GB RAM and 1.6TB of SSD, 1G ethernet
  34 nodes of 48 cores 96GB RAM and 1TB, infiniband
\end{frame}

\begin{frame}
  \frametitle{Current Storage}
  348TB EOS for ALICE
  252 TB EOS for ATLAS
  107 TB lustre for 34 nodes.
\end{frame}

\begin{frame}
  \frametitle{Current Performance}

\end{frame}

\begin{frame}
  \frametitle{Availability / Reliability}
  wlcg, egi, alice, atlas, chpc(zabbix/grafana).
\end{frame}

\begin{frame}
  \frametitle{upgrades}
  puppify, stabilise, collaborate with aaroc.
\end{frame}

\section{SAGrid, user analysis}
\begin{frame}
\frametitle{PROOF}
\ldots\ldots\ldots\ldots
\end{frame}


\begin{frame}
\frametitle{SAGrid and AAROC}
\ldots\ldots\ldots\ldots
\end{frame}

\section{Tier1}

\begin{frame}
\frametitle{Technical Requirements} 

\end{frame}

\begin{frame}
\frametitle{People Requirements} 
24x7 operation.
storage, hpc, support.
operators on call.
wlcg membership
meetings, meetings, meetings.
\end{frame}


\end{document}

